### 2015-03-19 evaluation.tex
updated table

When running \corral on its own, it can potentially report a spurious race (that \whoop does not report), because \corral is not enhanced with domain-specific information that \whoop uses to discard spurious races. Using \whoop + \corral, though, will inherently discard spurious data races (assuming a precise environmental model).

@@

When \corral on its own tries to analyse the machzwd watchdog driver it explodes, because in some entry point pairs it attempts to analyse a large number of memory regions. For example for the entry point pair write vs init, it instruments interleavings at 26 different memory regions in a single invocation of \corral, which required approximately 1000 seconds to analyse. The same entry point pair is found race-free by \whoop. Using this information in \corral with the \yieldmr instrumentation, the pair takes less than a second to analyse. The \yieldcoarse instrumentation does not perform as well, because it works in the binary granularity of racy or non-racy entry points.

>>>>

%When running \corral on its own, it can potentially report a spurious race (that \whoop does not report), because \corral is not enhanced with domain-specific information that \whoop uses to discard spurious races. Using \whoop + \corral, though, will inherently discard spurious data races (assuming a precise environmental model).

@@

%When \corral on its own tries to analyse the machzwd watchdog driver it explodes, because in some entry point pairs it attempts to analyse a large number of memory regions. For example for the entry point pair write vs init, it instruments interleavings at 26 different memory regions in a single invocation of \corral, which required approximately 1000 seconds to analyse. The same entry point pair is found race-free by \whoop. Using this information in \corral with the \yieldmr instrumentation, the pair takes less than a second to analyse. The \yieldcoarse instrumentation does not perform as well, because it works in the binary granularity of racy or non-racy entry points.
